Counting infinitely by Oritatami co-transcriptional folding

### 2019-08-26 paper.tex
writting zag pass...

Let us see how the subsequence $(FLHR)^kF$ folds into a zig; for $k=1$ and the current value 0 see Fig.~\ref{fig:counter1stzig}.
The zig is initially fed with carry by being forced to start folding at the bottom and the carry is propagated by modules F, L, and R in the way just explained.
The first instance of H is thus fed with carry and folds into \texttt{H01} if the bit encoded above is 0, as illustrated in Fig.~\ref{fig:counter1stzig}, or \texttt{H11} if the bit is rather 1.
\texttt{H01} ends at the top, corresponding to no-carry.
This absence of carry propagates through the succeeding modules leftward.
As a result, the zig ends, or more precisely an instance of F ends folding at the bottom if the current value is overflowed (Fig.~\ref{fig:overflowex1}), or at the top otherwise. (Fig.~\ref{fig:counter1stzig}).
An instance of L is to be transcribed next.
It folds either into \texttt{Lcrn} for (normal) carriage-return unless the current value is overflowed, or into \texttt{Lbe} at an overflow.
% Lbeの後の話 Lcreまで

>>>>

Let us see how the subsequence $(FLHR)^kF$ folds into a zig; for $k=1$ and the current value 0, see Fig.~\ref{fig:counter1stzig}.
The zig is initially fed with carry by being forced to start folding at the bottom and the carry is propagated through the first instances of F and L in the way just explained toward the first instance of H.
This H is thus fed with carry and folds into \texttt{H01} if the bit encoded above is 0, as illustrated in Fig.~\ref{fig:counter1stzig}, or \texttt{H11} if the bit is rather 1.
\texttt{H01} ends at the top, corresponding to no-carry.
This absence of carry propagates through the succeeding modules leftward.
As a result, the zig ends, or more precisely an instance of F ends folding at the bottom if the current value is overflowed (Fig.~\ref{fig:overflowex1}), or at the top otherwise. (Fig.~\ref{fig:counter1stzig}).
An instance of L is to be transcribed next.
It folds either into \texttt{Lcrn} for (normal) carriage-return unless the current value is overflowed, or into \texttt{Lbe} at an overflow.

\subsubsection{In the zag ($\rightarrow$)}
Here, the value incremented in the previous zig is formatted so as to be exposed below in the format \eqref{eq:zagencoding} for the next zig.
A subsequence $(HRFL)^kH$ of the transcript folds into the zag, where $k$ is the bit width of the incremented value.
Both of the bricks of L for carriage-return, i.e., \texttt{Lcrn} and \texttt{Lcre}, ends at the bottom so that zags start at the bottom.
The first instances of H and R fold into \texttt{Hn} and \texttt{Rb}, respectively.
Hence, the next F starts at the bottom and takes the brick \texttt{F}$y$ under the module H  that takes the brick \texttt{H}$xc$ in the previous zig, where $y$ is the output of the module, that is, $y = (x+c) \mod 2$.
Both of these bricks \texttt{F0} and \texttt{F1} end at the bottom so that the instance of L folds into \texttt{Lbn}.

% Lbeの後の話 Lcreまで
In the case of overflow, instance of H,  R, and F are transcribed following \texttt{Lbc} and they fold into \texttt{He1}, \texttt{Rb}, and \texttt{Fnb}, respectively.
Next instance of L which is transcribed after \texttt{Fnb} carriage-return for the next zag.
However, if its instance turn, Turn Signal must be present around there so the top of \texttt{Fnb} is given the role of Turn Signal.
Unless the count overflows, there is a brick above \texttt{Fnb} as shown in Fig.~\ref{fig:overflowex1}, so the top of \texttt{Fnb} is hidden, but when it overflows, Turn Signal is exposed.
